Optimal Particle Paths Around Points in $\R^2$ with Constrained Acceleration

### 2013-09-29 cone_theorems.tex
Finish adding 3 cone proof.

Now we are finally able to tackle the model problem of optimal paths around cones. The cone problem we will solve will involve only 3 cones, but first we will solve a simpler but related problem of minimizing the path length around a quadrilateral.

@@

\begin{align}
  x_c& = w - \frac{l2}{2 \cos{\theta}}\\
  y_c& = \frac{l_2}{2} - \frac{l_2}{2 \sin{\theta}}\\
  l_{AB}& = \sqrt{x_c^2 + y_c^2}\\
  & = \sqrt{ \paren{\frac{l_1}{2} - \frac{l_2}{2 \cos\theta}}^2 + \paren{w - \frac{l_2}{2 \sin\theta}}^2 }\\
  l_{BC}& = l2\\
  l_{CD}& = \sqrt{\paren{\frac{l_1}{2} + \frac{l_2}{2 \cos\theta}}^2 + \paren{w - \frac{l_2}{2 \sin\theta}}^2 }
\end{align}

@@

Given a particle with zero tangential acceleration and bounded centripetal acceleration, $a_c \le a_{c,max}$, and a cone setup consisting of 3 cones, A, B, and C, at locations $\bvec{X_A}$, $\bvec{X_B}$, and $\bvec{X_C}$ as is shown in Figure \ref{fig:3-cones}.

\includefig{3_cones.eps}{3 Cone setup}{3-cones}

The optimal path [TODO]

@@

\begin{proof}
Since speed is constant, the optimal path will be the shortest path. The optimal path is of the form, tr. Thus, the problem reduces to a trigonometric problem.

@@

The turn must touch the cone B, otherwise the trajectory will either not go around the cone, or be longer than necessary. Therefor, the center of the turn must be a distance $r$ away from

@@

\begin{align*}
x_c = x_B - r \cos{\alpha_c}\\
y_c = y_B - r \sin{\alpha_c}\\
l_1& = \sqrt{d_c - r}\\
l_2& = r \paren{\alpha_c - \tan^{-1}\paren{\frac{y_c}{x_c}}}\\
\end{align*}
\end{proof}

>>>>

Now we are finally able to tackle the model problem of optimal paths around cones. First we will solve a simpler but related problem of minimizing the path length around a quadrilateral.

@@

\begin{align}
  x_c& = w - \frac{l_2}{2 \cos{\theta}}\\
  y_c& = \frac{l_2}{2} - \frac{l_2}{2 \sin{\theta}}\\
  l_{AB}& = \sqrt{x_c^2 + y_c^2}\\
  & = \sqrt{ \paren{\frac{l_1}{2} - \frac{l_2}{2 \cos\theta}}^2 + \paren{w - \frac{l_2}{2 \sin\theta}}^2 }\\
  l_{BC}& = l_2\\
  l_{CD}& = \sqrt{\paren{\frac{l_1}{2} + \frac{l_2}{2 \cos\theta}}^2 + \paren{w - \frac{l_2}{2 \sin\theta}}^2 }
\end{align}

@@

Given a particle with zero tangential acceleration and bounded centripetal acceleration, $a_c \le a_{c,max}$, and a cone setup consisting of 3 cones, A, B, and C, at locations $\bvec{X_A}$, $\bvec{X_B}$, and $\bvec{X_C}$ as is shown in Figure \ref{fig:3-cones}

\includefig{3_cones.eps}{3 cone setup}{3-cones}

the optimal path around the cones is shown in Figure \ref{fig:3-cones-path}

\includefig{3_cones_path.eps}{3 cone optimal path}{3-cones-path}

@@

\begin{proof}
[TODO: Finish proof]

Since speed is constant, the optimal path will be the shortest path. By Corollary \ref{corr:optimal-path-fix-s}, the optimal path can only include line segments and circular sections. Thus, the problem reduces to a trigonometric problem.

The turn must touch cone B, otherwise the trajectory will either not go around the cone, or be longer than necessary. Therefor, the center of the turn, c, must be a distance $r$ away from cone B.

@@

Now that c is defined by $\alpha$, let us determine the total path length as a function of $\alpha$.

@@

\begin{align*}
x_c& = x_B - r \cos{\alpha_c}\\
y_c& = y_B - r \sin{\alpha_c}\\
l_1& = \sqrt{d_c - r}\\
l_2& = r \paren{\alpha_c - \tan^{-1}\paren{\frac{y_c}{x_c}}}\\
\end{align*}
\end{proof}

### 2013-09-29 path_theorems.tex
Finish adding 3 cone proof.

\begin{corollary}
Given a 2-dimensional particle, $p$, with bounded centripetal acceleration, $a_c \le a_{c,max}$ and zero tangential acceleration, every valid optimal trajectory is constructed from line segments and circular sections of radius $R_{min}$, that are tangent at their intersections.
\end{corollary}

>>>>

\begin{corollary}\label{cor:optimal-path-fix-s}
Given a 2-dimensional particle, $p$, with bounded centripetal acceleration, $a_c \le a_{c,max}$ and zero tangential acceleration, every valid optimal trajectory is constructed from line segments and circular sections of radius $R_{min}$, that are tangent at their intersections.
\end{corollary}
